---
title: "UFPs (Ultrafine Particles) Spatial Analysis for CNG and Diesel vehicle for mobile monitoring"
author: "Adithi R. Upadhya - ILK Labs"
date: "7/12/2020"
output: 
  html_document:
    df_print: paged
    code_folding: hide
    fig_width: 8
    fig_height: 6
    toc: true
    toc_float: true
    number_sections: true
    fig_caption: true
theme: yeti
---
<style type="text/css">
body{
  font-family: Candara;
  font-size: 13pt;
}
code.r{
    font-size: 12pt;
}
pre { 
    font-size: 12pt;
}
</style>


```{r setup, include = FALSE}
library(ggplot2)
library(dplyr)
library(lubridate)
library(ggrepel)
library(rgdal)
library(sp)
library(raster)
library(sf)
library(leaflet)
library(purrr)
library(scales)
risk.bins <- c(0, 5000, 10000, 20000, 40000, 70000, 100000, 150000, 200000, 500000)
pal <- colorBin( "Spectral", bins = risk.bins, na.color = "#808080", reverse = TRUE)
p <- c(0.1, 0.25, 0.5, 0.75, 0.9)
p_names <- map_chr(p, ~paste0(.x*100, "%"))
p_funs <- map(p, ~partial(quantile, probs = .x, na.rm = TRUE)) %>%
      set_names(nm = p_names)
```

# Study Area Spatial Analysis

**All the data used here is from the snapped 30 m road segment Median of means, collected for Ultrafine Particles.**

```{r include = FALSE, warning = FALSE, message = FALSE}
setwd("D:/Dropbox/APMfull/All_Data_CNG_Dsl/Diesel_CNG_layer")
cbd_cng_map <- readOGR("Corrected_Median_Means_Final_CBD_CNG_Layer.shp", layer = "Corrected_Median_Means_Final_CBD_CNG_Layer")
kan_cng_map <- readOGR("Corrected_Median_Means_Final_KAN_CNG_Layer.shp", layer = "Corrected_Median_Means_Final_KAN_CNG_Layer")
mal1_cng_map <- readOGR("Corrected_Median_Means_Final_MAL1_CNG_Layer.shp", layer = "Corrected_Median_Means_Final_MAL1_CNG_Layer")
mal2_cng_map <- readOGR("Corrected_Median_Means_Final_MAL2_CNG_Layer.shp", layer = "Corrected_Median_Means_Final_MAL2_CNG_Layer")
cng_map <- bind(cbd_cng_map, kan_cng_map, mal1_cng_map, mal2_cng_map)
cng_map <- spTransform(cng_map, CRS("+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0 "))
cng <- st_as_sf(cng_map) 
cng <- cng %>%
  data.frame(cng) %>%
  dplyr::select(UID, Med_CPC) 
names(cng) <- c("UID", "UFPs_CNG")
cbd_dsl_map <- readOGR("Corrected_Median_Means_Final_CBD_Diesel_Layer.shp", layer = "Corrected_Median_Means_Final_CBD_Diesel_Layer")
kan_dsl_map <- readOGR("Corrected_Median_Means_Final_KAN_Diesel_Layer.shp", layer = "Corrected_Median_Means_Final_KAN_Diesel_Layer")
mal1_dsl_map <- readOGR("Corrected_Median_Means_Final_MAL1_Diesel_Layer.shp", layer = "Corrected_Median_Means_Final_MAL1_Diesel_Layer")
mal2_dsl_map <- readOGR("Corrected_Median_Means_Final_MAL2_Diesel_Layer.shp", layer = "Corrected_Median_Means_Final_MAL2_Diesel_Layer")
dsl_map <- bind(cbd_dsl_map, kan_dsl_map, mal1_dsl_map, mal2_dsl_map)
dsl_map <- spTransform(dsl_map, CRS("+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0 "))
dsl <- st_as_sf(dsl_map) 
dsl <- dsl %>%
  data.frame(dsl) %>%
  dplyr::select(UID, Med_CPC) 
names(dsl) <- c("UID", "UFPs_Dsl")
final <- left_join(cng, dsl, by = "UID")
final1 <- final
final$UID <- NULL
```

## Summary of the data 
 
```{r fig.align = "center", warning = FALSE, message = FALSE, fig.cap = "\\label{fig:figs}Fig 1: Frequency distribution for the CNG Median of Means map"}
y <- ggplot(data = final, aes(x = UFPs_CNG)) + geom_histogram(colour = "#b87333", fill = "#b87333") +
  theme_classic() + labs(x = "UFPs_CNG", y = "count") +
  scale_x_continuous() +
  scale_y_continuous() +
  theme(legend.text = element_text(size = 14),
        plot.subtitle = element_text(size = 10, face = "bold"), 
        axis.title = element_text(size = 18, colour = "black", face = "bold"), 
        axis.text = element_text(size = 14, colour = "black", face = "bold"),
        panel.border = element_rect(colour = "black", fill = NA, size = 1), 
        legend.position = "none",
        strip.background = element_blank(), strip.text = element_blank()) + 
  geom_text(aes(label = paste("N = ",sum(!is.na(final$UFPs_CNG)))), x = Inf, y = Inf, hjust = 1, vjust = 2, colour = "black", size = 7)  
y
```

```{r fig.align = "center", warning = FALSE, message = FALSE, fig.cap = "\\label{fig:figs}Fig 2: Frequency distribution for the Diesel Median of Means map"}
y <- ggplot(data = final, aes(x = UFPs_Dsl)) + geom_histogram(colour = "#b87333", fill = "#b87333") +
  theme_classic() + labs(x = "UFPs_Dsl", y = "count") +
  scale_x_continuous(limits = c(0, NA), expand = c(0, 0)) +
  scale_y_continuous() +
  theme(legend.text = element_text(size = 14),
        plot.subtitle = element_text(size = 10, face = "bold"), 
        axis.title = element_text(size = 18, colour = "black", face = "bold"), 
        axis.text = element_text(size = 14, colour = "black", face = "bold"),
        panel.border = element_rect(colour = "black", fill = NA, size = 1), 
        legend.position = "none",
        strip.background = element_blank(), strip.text = element_blank()) + 
  geom_text(aes(label = paste("N = ",sum(!is.na(final$UFPs_Dsl)))), x = Inf, y = Inf, hjust = 1, vjust = 2, colour = "black", size = 7)  
y
```

```{r cols.print = 13}
names(final) <- c("UFPs_CNG",  "UFPs_Dsl")
columns <-c("UFPs_CNG", "UFPs_Dsl")
final$UFPs_CNG <- as.numeric(as.character(final$UFPs_CNG))
final$UFPs_Dsl <- as.numeric(as.character(final$UFPs_Dsl))
tmp <- do.call(data.frame,
               list(Mean = apply(final, 2, mean, na.rm = TRUE),
                    SD = apply(final, 2, sd, na.rm = TRUE), 
                    Median = apply(final, 2, median, na.rm = TRUE),
                    IQR = apply(final, 2, IQR, na.rm = TRUE),
                    Min = apply(final, 2, min, na.rm = TRUE),
                    Max = apply(final, 2, max, na.rm = TRUE),
                    p1 = apply(final, 2, quantile, probs = c(0.01), na.rm = TRUE),
                    p10 = apply(final, 2, quantile, probs = c(0.1), na.rm = TRUE),
                    p25 = apply(final, 2, quantile, probs = c(0.25), na.rm = TRUE),
                    p75 = apply(final, 2, quantile, probs = c(0.75), na.rm = TRUE),
                    p90 = apply(final, 2, quantile, probs = c(0.9),  na.rm = TRUE),
                    p99 = apply(final, 2, quantile, probs = c(0.99), na.rm = TRUE),
                    Total_non_NA = apply(final, 2, function(x) { length(which(!is.na(x))) })))
tmp$Mean <- round(as.numeric(tmp$Mean), digits = 2)
tmp$IQR <- round(as.numeric(tmp$IQR), digits = 2)
tmp$Median <- round(as.numeric(tmp$Median), digits = 2)
tmp$Min <- round(as.numeric(tmp$Min), digits = 2)
tmp$Max <- round(as.numeric(tmp$Max), digits = 2)
tmp$p10 <- round(as.numeric(tmp$p10), digits = 2)
tmp$SD <- round(as.numeric(tmp$SD), digits = 2)
tmp$p90 <- round(as.numeric(tmp$p90), digits = 2)
tmp$p75 <- round(as.numeric(tmp$p75), digits = 2)
tmp$p99 <- round(as.numeric(tmp$p99), digits = 2)
tmp$p1 <- round(as.numeric(tmp$p1), digits = 2)
tmp$p25 <- round(as.numeric(tmp$p25), digits = 2)
tmp

```

## Median of means map in Study Area for CNG car

```{r fig.align = "center", fig.cap = "\\label{fig:figs}Fig 3: CNG Median of Means map"}
leaflet(cng_map) %>% 
  addProviderTiles(providers$Stamen.TonerLite) %>%
  addPolylines(weight = 3, color = ~pal(cng_map$Med_CPC)) %>%
      addLegend("bottomright", pal = pal, values = ~cng_map$Med_CPC,  title = paste("CNG UFPs Map")) 
```

## Median of means map in Study Area for Diesel car

```{r fig.align = "center", fig.cap = "\\label{fig:figs}Fig 4: Diesel Median of Means map"}
leaflet(dsl_map) %>% 
  addProviderTiles(providers$Stamen.TonerLite) %>%
  addPolylines(weight = 3, color = ~pal(dsl_map$Med_CPC)) %>%
      addLegend("bottomright", pal = pal, values = ~dsl_map$Med_CPC,  title = paste("Diesel UFPs Map")) 
```

## t-test for UFPs_CNG and UFPs_Dsl data 

```{r message = FALSE, warning = FALSE}
t_test <- t.test(final$UFPs_CNG, final$UFPs_Dsl)
a <- t_test$p.value
b <- round(t_test$estimate[1], digits = 2)
c <- round(t_test$estimate[2], digits=2)
e <- round(as.numeric(t_test$parameter), digits = 2)
f <- round(as.numeric(t_test$statistic), digits = 2)
t_test
```

# CBD Spatial Analysis

```{r include = FALSE, warning = FALSE, message = FALSE}
setwd("D:/Dropbox/APMfull/All_Data_CNG_Dsl/Diesel_CNG_layer")
cbd_cng_map <- readOGR("Corrected_Median_Means_Final_CBD_CNG_Layer.shp", layer = "Corrected_Median_Means_Final_CBD_CNG_Layer")
cbd_cng_map <- spTransform(cbd_cng_map, CRS("+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0 "))
cbd_cng <- st_as_sf(cbd_cng_map) 
cbd_cng <- cbd_cng %>%
  data.frame(cbd_cng)  %>%
  dplyr::select(Road_ID, Med_CPC) 
names(cbd_cng) <- c("Road_ID", "UFPs_CNG")
cbd_dsl_map <- readOGR("Corrected_Median_Means_Final_CBD_Diesel_Layer.shp", layer = "Corrected_Median_Means_Final_CBD_Diesel_Layer")
cbd_dsl_map <- spTransform(cbd_dsl_map, CRS("+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0 "))
cbd_dsl <- st_as_sf(cbd_dsl_map) 
cbd_dsl <- cbd_dsl %>%
  data.frame(cbd_dsl) %>%
  dplyr::select(Road_ID, Med_CPC) 
names(cbd_dsl) <- c("Road_ID", "UFPs_Dsl")
CBD_final <- left_join(cbd_cng, cbd_dsl, by = "Road_ID")
CBD_final$Road_ID <- NULL
```

## Summary of the data

**Using Median of Means map for CNG car with 22 passes.**

```{r fig.align = "center", warning = FALSE, message = FALSE, fig.cap = "\\label{fig:figs}Fig 5: Frequency distribution for the CNG Median of Means map"}
y <- ggplot(data = CBD_final, aes(x = UFPs_CNG)) + geom_histogram(colour = "#b87333", fill = "#b87333") +
  theme_classic() + labs(x = "UFPs_CNG", y = "count") +
  scale_x_continuous() +
  scale_y_continuous() +
  theme(legend.text = element_text(size = 14),
        plot.subtitle = element_text(size = 10, face = "bold"), 
        axis.title = element_text(size = 18, colour = "black", face = "bold"), 
        axis.text = element_text(size = 14, colour = "black", face = "bold"),
        panel.border = element_rect(colour = "black", fill = NA, size = 1), 
        legend.position = "none",
        strip.background = element_blank(), strip.text = element_blank()) + 
  geom_text(aes(label = paste("N = ",sum(!is.na(CBD_final$UFPs_CNG)))), x = Inf, y = Inf, hjust = 1, vjust = 2, colour = "black", size = 7)  
y
```

**Using Median of Means map for Diesel car with 6 passes.**

```{r fig.align = "center", warning = FALSE, message = FALSE, fig.cap = "\\label{fig:figs}Fig 6: Frequency distribution for the Diesel Median of Means map"}
y <- ggplot(data = CBD_final, aes(x = UFPs_Dsl)) + geom_histogram(colour = "#b87333", fill = "#b87333") +
  theme_classic() + labs(x = "UFPs_Dsl", y = "count") +
  scale_x_continuous() +
  scale_y_continuous() +
  theme(legend.text = element_text(size = 14),
        plot.subtitle = element_text(size = 10, face = "bold"), 
        axis.title = element_text(size = 18, colour = "black", face = "bold"), 
        axis.text = element_text(size = 14, colour = "black", face = "bold"),
        panel.border = element_rect(colour = "black", fill = NA, size = 1), 
        legend.position = "none",
        strip.background = element_blank(), strip.text = element_blank()) + 
  geom_text(aes(label = paste("N = ",sum(!is.na(CBD_final$UFPs_Dsl)))), x = Inf, y = Inf, hjust = 1, vjust = 2, colour = "black", size = 7) 
y
```

```{r cols.print = 13}
names(CBD_final) <- c("UFPs_CNG",  "UFPs_Dsl")
columns <-c("UFPs_CNG",  "UFPs_Dsl")
CBD_final$UFPs_CNG <- as.numeric(as.character(CBD_final$UFPs_CNG))
CBD_final$UFPs_Dsl <- as.numeric(as.character(CBD_final$UFPs_Dsl))
tmp <- do.call(data.frame,
               list(Mean = apply(CBD_final, 2, mean, na.rm = TRUE),
                    SD = apply(CBD_final, 2, sd, na.rm = TRUE), 
                    Median = apply(CBD_final, 2, median, na.rm = TRUE),
                    IQR = apply(CBD_final, 2, IQR, na.rm = TRUE),
                    Min = apply(CBD_final, 2, min, na.rm = TRUE),
                    Max = apply(CBD_final, 2, max, na.rm = TRUE),
                    p1 = apply(CBD_final, 2, quantile, probs = c(0.01), na.rm = TRUE),
                    p10 = apply(CBD_final, 2, quantile, probs = c(0.1), na.rm = TRUE),
                    p25 = apply(CBD_final, 2, quantile, probs = c(0.25), na.rm = TRUE),
                    p75 = apply(CBD_final, 2, quantile, probs = c(0.75), na.rm = TRUE),
                    p90 = apply(CBD_final, 2, quantile, probs = c(0.9),  na.rm = TRUE),
                    p99 = apply(CBD_final, 2, quantile, probs = c(0.99), na.rm = TRUE),
                    Total_non_NA = apply(CBD_final, 2, function(x) { length(which(!is.na(x))) })))
tmp$Mean <- round(as.numeric(tmp$Mean), digits = 2)
tmp$IQR <- round(as.numeric(tmp$IQR), digits = 2)
tmp$Median <- round(as.numeric(tmp$Median), digits = 2)
tmp$Min <- round(as.numeric(tmp$Min), digits = 2)
tmp$Max <- round(as.numeric(tmp$Max), digits = 2)
tmp$p10 <- round(as.numeric(tmp$p10), digits = 2)
tmp$SD <- round(as.numeric(tmp$SD), digits = 2)
tmp$p90 <- round(as.numeric(tmp$p90), digits = 2)
tmp$p75 <- round(as.numeric(tmp$p75), digits = 2)
tmp$p99 <- round(as.numeric(tmp$p99), digits = 2)
tmp$p1 <- round(as.numeric(tmp$p1), digits = 2)
tmp$p25 <- round(as.numeric(tmp$p25), digits = 2)
tmp

```

## Median of means map in CBD for CNG car

```{r fig.align="center", fig.cap = "\\label{fig:figs}Fig 7: CNG Median of Means map"}
leaflet(cbd_cng_map) %>% 
  addProviderTiles(providers$Stamen.TonerLite) %>%
  addPolylines(weight = 7, color = ~pal(cbd_cng_map$Med_CPC)) %>%
      addLegend("bottomright", pal = pal, values = ~cbd_cng_map$Med_CPC,  title = paste("CNG UFPs Map"))
 
```

## Median of means map in CBD for Diesel car

```{r fig.align="center", fig.cap = "\\label{fig:figs}Fig 8: Diesel Median of Means map"}
leaflet(cbd_dsl_map) %>% 
  addProviderTiles(providers$Stamen.TonerLite) %>%
  addPolylines(weight = 7, color = ~pal(cbd_dsl_map$Med_CPC)) %>%
      addLegend("bottomright", pal = pal, values = ~cbd_dsl_map$Med_CPC,  title = paste("Diesel UFPs Map"))
 
```

## t-test for UFPs_CNG and UFPs_Dsl data  

```{r message = FALSE, warning = FALSE}
t_test <- t.test(CBD_final$UFPs_CNG, CBD_final$UFPs_Dsl)
a <- t_test$p.value
b <- round(t_test$estimate[1], digits = 2)
c <- round(t_test$estimate[2], digits=2)
e <- round(as.numeric(t_test$parameter), digits = 2)
f <- round(as.numeric(t_test$statistic), digits = 2)
t_test
```


# Kannuru Spatial Analysis

```{r include = FALSE, warning = FALSE, message = FALSE}
setwd("D:/Dropbox/APMfull/All_Data_CNG_Dsl/Diesel_CNG_layer")
kan_cng_map <- readOGR("Corrected_Median_Means_Final_KAN_CNG_Layer.shp", layer = "Corrected_Median_Means_Final_KAN_CNG_Layer")
kan_cng_map <- spTransform(kan_cng_map, CRS("+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0 "))
kan_cng <- st_as_sf(kan_cng_map) 
kan_cng <- kan_cng %>%
  data.frame(kan_cng)  %>%
  dplyr::select(Road_ID, Med_CPC) 
names(kan_cng) <- c("Road_ID", "UFPs_CNG")
kan_dsl_map <- readOGR("Corrected_Median_Means_Final_KAN_Diesel_Layer.shp", layer = "Corrected_Median_Means_Final_KAN_Diesel_Layer")
kan_dsl_map <- spTransform(kan_dsl_map, CRS("+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0 "))
kan_dsl <- st_as_sf(kan_dsl_map) 
kan_dsl <- kan_dsl %>%
  data.frame(kan_dsl) %>%
  dplyr::select(Road_ID, Med_CPC) 
names(kan_dsl) <- c("Road_ID", "UFPs_Dsl")
KAN_final <- left_join(kan_cng, kan_dsl, by = "Road_ID")
KAN_final$Road_ID <- NULL
```

## Summary of the data

**Using Median of Means map for CNG car with 22 passes.**

```{r fig.align = "center", warning = FALSE, message = FALSE, fig.cap = "\\label{fig:figs}Fig 9: Frequency distribution for the CNG Median of Means map"}
y <- ggplot(data = KAN_final, aes(x = UFPs_CNG)) + geom_histogram(colour = "#b87333", fill = "#b87333") +
  theme_classic() + labs(x = "UFPs_CNG", y = "count") +
  scale_x_continuous() +
  scale_y_continuous() +
  theme(legend.text = element_text(size = 14),
        plot.subtitle = element_text(size = 10, face = "bold"), 
        axis.title = element_text(size = 18, colour = "black", face = "bold"), 
        axis.text = element_text(size = 14, colour = "black", face = "bold"),
        panel.border = element_rect(colour = "black", fill = NA, size = 1), 
        legend.position = "none",
        strip.background = element_blank(), strip.text = element_blank()) + 
  geom_text(aes(label = paste("N = ",sum(!is.na(KAN_final$UFPs_CNG)))), x = Inf, y = Inf, hjust = 1, vjust = 2, colour = "black", size = 7) 
y
```

**Using Median of Means map for Diesel car with 7 passes.**

```{r fig.align = "center", warning = FALSE, message = FALSE, fig.cap = "\\label{fig:figs}Fig 10: Frequency distribution for the Diesel Median of Means map"}
y <- ggplot(data = KAN_final, aes(x = UFPs_Dsl)) + geom_histogram(colour = "#b87333", fill = "#b87333") +
  theme_classic() + labs(x = "UFPs_Dsl", y = "count") +
  scale_x_continuous(limits = c(0, NA), expand = c(0, 0)) +
  scale_y_continuous() +
  theme(legend.text = element_text(size = 14),
        plot.subtitle = element_text(size = 10, face = "bold"), 
        axis.title = element_text(size = 18, colour = "black", face = "bold"), 
        axis.text = element_text(size = 14, colour = "black", face = "bold"),
        panel.border = element_rect(colour = "black", fill = NA, size = 1), 
        legend.position = "none",
        strip.background = element_blank(), strip.text = element_blank()) + 
  geom_text(aes(label = paste("N = ",sum(!is.na(KAN_final$UFPs_Dsl)))), x = Inf, y = Inf, hjust = 1, vjust = 2, colour = "black", size = 7) 
y
```

```{r cols.print = 13}
names(KAN_final) <- c("UFPs_CNG",  "UFPs_Dsl")
columns <-c("UFPs_CNG",  "UFPs_Dsl")
KAN_final$UFPs_CNG <- as.numeric(as.character(KAN_final$UFPs_CNG))
KAN_final$UFPs_Dsl <- as.numeric(as.character(KAN_final$UFPs_Dsl))
tmp <- do.call(data.frame,
               list(Mean = apply(KAN_final, 2, mean, na.rm = TRUE),
                    SD = apply(KAN_final, 2, sd, na.rm = TRUE), 
                    Median = apply(KAN_final, 2, median, na.rm = TRUE),
                    IQR = apply(KAN_final, 2, IQR, na.rm = TRUE),
                    Min = apply(KAN_final, 2, min, na.rm = TRUE),
                    Max = apply(KAN_final, 2, max, na.rm = TRUE),
                    p1 = apply(KAN_final, 2, quantile, probs = c(0.01), na.rm = TRUE),
                    p10 = apply(KAN_final, 2, quantile, probs = c(0.1), na.rm = TRUE),
                    p25 = apply(KAN_final, 2, quantile, probs = c(0.25), na.rm = TRUE),
                    p75 = apply(KAN_final, 2, quantile, probs = c(0.75), na.rm = TRUE),
                    p90 = apply(KAN_final, 2, quantile, probs = c(0.9),  na.rm = TRUE),
                    p99 = apply(KAN_final, 2, quantile, probs = c(0.99), na.rm = TRUE),
                    Total_non_NA = apply(KAN_final, 2, function(x) { length(which(!is.na(x))) })))
tmp$Mean <- round(as.numeric(tmp$Mean), digits = 2)
tmp$IQR <- round(as.numeric(tmp$IQR), digits = 2)
tmp$Median <- round(as.numeric(tmp$Median), digits = 2)
tmp$Min <- round(as.numeric(tmp$Min), digits = 2)
tmp$Max <- round(as.numeric(tmp$Max), digits = 2)
tmp$p10 <- round(as.numeric(tmp$p10), digits = 2)
tmp$SD <- round(as.numeric(tmp$SD), digits = 2)
tmp$p90 <- round(as.numeric(tmp$p90), digits = 2)
tmp$p75 <- round(as.numeric(tmp$p75), digits = 2)
tmp$p99 <- round(as.numeric(tmp$p99), digits = 2)
tmp$p1 <- round(as.numeric(tmp$p1), digits = 2)
tmp$p25 <- round(as.numeric(tmp$p25), digits = 2)
tmp

```

## Median of means map in Kannuru for CNG car

```{r fig.align = "center", fig.cap = "\\label{fig:figs}Fig 11: CNG Median of Means map"}
leaflet(kan_cng_map) %>% 
  addProviderTiles(providers$Stamen.TonerLite) %>%
  addPolylines(weight = 7, color = ~pal(kan_cng_map$Med_CPC)) %>%
      addLegend("bottomright", pal = pal, values = ~kan_cng_map$Med_CPC,  title = paste("CNG UFPs Map"))
 
```

## Median of means map in Kannuru for Diesel car

```{r fig.align = "center", fig.cap = "\\label{fig:figs}Fig 12: Diesel Median of Means map"}
leaflet(kan_dsl_map) %>% 
  addProviderTiles(providers$Stamen.TonerLite) %>%
  addPolylines(weight = 7, color = ~pal(kan_dsl_map$Med_CPC)) %>%
      addLegend("bottomright", pal = pal, values = ~kan_dsl_map$Med_CPC,  title = paste("Diesel UFPs Map"))
 
```

## t-test for UFPs_CNG and UFPs_Dsl data 

```{r message = FALSE, warning = FALSE}
t_test <- t.test(KAN_final$UFPs_CNG, KAN_final$UFPs_Dsl)
a <- t_test$p.value
b <- round(t_test$estimate[1], digits = 2)
c <- round(t_test$estimate[2], digits=2)
e <- round(as.numeric(t_test$parameter), digits = 2)
f <- round(as.numeric(t_test$statistic), digits = 2)
t_test
```


# Malleshwaram 1 Spatial Analysis

```{r include = FALSE, warning = FALSE, message = FALSE}
setwd("D:/Dropbox/APMfull/All_Data_CNG_Dsl/Diesel_CNG_layer")
mal1_cng_map <- readOGR("Corrected_Median_Means_Final_MAL1_CNG_Layer.shp", layer = "Corrected_Median_Means_Final_MAL1_CNG_Layer")
mal1_cng_map <- spTransform(mal1_cng_map, CRS("+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0 "))
mal1_cng <- st_as_sf(mal1_cng_map) 
mal1_cng <- mal1_cng %>%
  data.frame(mal1_cng)  %>%
  dplyr::select(Road_ID, Med_CPC) 
names(mal1_cng) <- c("Road_ID", "UFPs_CNG")
mal1_dsl_map <- readOGR("Corrected_Median_Means_Final_MAL1_Diesel_Layer.shp", layer = "Corrected_Median_Means_Final_MAL1_Diesel_Layer")
mal1_dsl_map <- spTransform(mal1_dsl_map, CRS("+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0 "))
mal1_dsl <- st_as_sf(mal1_dsl_map) 
mal1_dsl <- mal1_dsl %>%
  data.frame(mal1_dsl) %>%
  dplyr::select(Road_ID, Med_CPC) 
names(mal1_dsl) <- c("Road_ID", "UFPs_Dsl")
MAL1_final <- left_join(mal1_cng, mal1_dsl, by = "Road_ID")
MAL1_final$Road_ID <- NULL

```

## Summary of the data

**Using Median of Means map for CNG car with 22 passes.**

```{r fig.align = "center", warning = FALSE, message = FALSE, fig.cap = "\\label{fig:figs}Fig 13: Frequency distribution for the CNG Median of Means map"}
y <- ggplot(data = MAL1_final, aes(x = UFPs_CNG)) + geom_histogram(colour = "#b87333", fill = "#b87333") +
  theme_classic() + labs(x = "UFPs_CNG", y = "count") +
  scale_x_continuous() +
  scale_y_continuous() +
  theme(legend.text = element_text(size = 14),
        plot.subtitle = element_text(size = 10, face = "bold"), 
        axis.title = element_text(size = 18, colour = "black", face = "bold"), 
        axis.text = element_text(size = 14, colour = "black", face = "bold"),
        panel.border = element_rect(colour = "black", fill = NA, size = 1), 
        legend.position = "none",
        strip.background = element_blank(), strip.text = element_blank()) + 
  geom_text(aes(label = paste("N = ",sum(!is.na(MAL1_final$UFPs_CNG)))), x = Inf, y = Inf, hjust = 1, vjust = 2, colour = "black", size = 7) 
y
```

**Using Median of Means map for Diesel car with 5 passes.**

```{r fig.align = "center", warning = FALSE, message = FALSE, fig.cap = "\\label{fig:figs}Fig 14: Frequency distribution for the Diesel Median of Means map"}
y <- ggplot(data = MAL1_final, aes(x = UFPs_Dsl)) + geom_histogram(colour = "#b87333", fill = "#b87333") +
  theme_classic() + labs(x = "UFPs_Dsl", y = "count") +
  scale_x_continuous(limits = c(0, NA), expand = c(0, 0)) +
  scale_y_continuous() +
  theme(legend.text = element_text(size = 14),
        plot.subtitle = element_text(size = 10, face = "bold"), 
        axis.title = element_text(size = 18, colour = "black", face = "bold"), 
        axis.text = element_text(size = 14, colour = "black", face = "bold"),
        panel.border = element_rect(colour = "black", fill = NA, size = 1), 
        legend.position = "none",
        strip.background = element_blank(), strip.text = element_blank()) + 
  geom_text(aes(label = paste("N = ",sum(!is.na(MAL1_final$UFPs_Dsl)))), x = Inf, y = Inf, hjust = 1, vjust = 2, colour = "black", size = 7) 
y
```

```{r cols.print = 13}
names(MAL1_final) <- c("UFPs_CNG",  "UFPs_Dsl")
columns <-c("UFPs_CNG",  "UFPs_Dsl")
MAL1_final$UFPs_CNG <- as.numeric(as.character(MAL1_final$UFPs_CNG))
MAL1_final$UFPs_Dsl <- as.numeric(as.character(MAL1_final$UFPs_Dsl))
tmp <- do.call(data.frame,
               list(Mean = apply(MAL1_final, 2, mean, na.rm = TRUE),
                    SD = apply(MAL1_final, 2, sd, na.rm = TRUE), 
                    Median = apply(MAL1_final, 2, median, na.rm = TRUE),
                    IQR = apply(MAL1_final, 2, IQR, na.rm = TRUE),
                    Min = apply(MAL1_final, 2, min, na.rm = TRUE),
                    Max = apply(MAL1_final, 2, max, na.rm = TRUE),
                    p1 = apply(MAL1_final, 2, quantile, probs = c(0.01), na.rm = TRUE),
                    p10 = apply(MAL1_final, 2, quantile, probs = c(0.1), na.rm = TRUE),
                    p25 = apply(MAL1_final, 2, quantile, probs = c(0.25), na.rm = TRUE),
                    p75 = apply(MAL1_final, 2, quantile, probs = c(0.75), na.rm = TRUE),
                    p90 = apply(MAL1_final, 2, quantile, probs = c(0.9),  na.rm = TRUE),
                    p99 = apply(MAL1_final, 2, quantile, probs = c(0.99), na.rm = TRUE),
                    Total_non_NA = apply(MAL1_final, 2, function(x) { length(which(!is.na(x))) })))
tmp$Mean <- round(as.numeric(tmp$Mean), digits = 2)
tmp$IQR <- round(as.numeric(tmp$IQR), digits = 2)
tmp$Median <- round(as.numeric(tmp$Median), digits = 2)
tmp$Min <- round(as.numeric(tmp$Min), digits = 2)
tmp$Max <- round(as.numeric(tmp$Max), digits = 2)
tmp$p10 <- round(as.numeric(tmp$p10), digits = 2)
tmp$SD <- round(as.numeric(tmp$SD), digits = 2)
tmp$p90 <- round(as.numeric(tmp$p90), digits = 2)
tmp$p75 <- round(as.numeric(tmp$p75), digits = 2)
tmp$p99 <- round(as.numeric(tmp$p99), digits = 2)
tmp$p1 <- round(as.numeric(tmp$p1), digits = 2)
tmp$p25 <- round(as.numeric(tmp$p25), digits = 2)
tmp

```

## Median of means map in Malleshwaram 1 for CNG car

```{r fig.align = "center", fig.cap = "\\label{fig:figs}Fig 15: CNG Median of Means map"}
leaflet(mal1_cng_map) %>% 
  addProviderTiles(providers$Stamen.TonerLite) %>%
  addPolylines(weight = 7, color = ~pal(mal1_cng_map$Med_CPC)) %>%
      addLegend("bottomright", pal = pal, values = ~mal1_cng_map$Med_CPC,  title = paste("CNG UFPs Map")) 
 
```

## Median of means map in Malleshwaram 1 for Diesel car

```{r fig.align = "center", fig.cap = "\\label{fig:figs}Fig 16: Diesel Median of Means map"}
leaflet(mal1_dsl_map) %>% 
  addProviderTiles(providers$Stamen.TonerLite) %>%
  addPolylines(weight = 7, color = ~pal(mal1_dsl_map$Med_CPC)) %>%
      addLegend("bottomright", pal = pal, values = ~mal1_dsl_map$Med_CPC,  title = paste("Diesel UFPs Map")) 
 
```

## t-test for UFPs_CNG and UFPs_Dsl data 

```{r message = FALSE, warning = FALSE}
t_test <- t.test(MAL1_final$UFPs_CNG, MAL1_final$UFPs_Dsl)
a <- t_test$p.value
b <- round(t_test$estimate[1], digits = 2)
c <- round(t_test$estimate[2], digits=2)
e <- round(as.numeric(t_test$parameter), digits = 2)
f <- round(as.numeric(t_test$statistic), digits = 2)
t_test
```


# Malleshwaram 2 Spatial Analysis

```{r include = FALSE, warning = FALSE, message = FALSE}
setwd("D:/Dropbox/APMfull/All_Data_CNG_Dsl/Diesel_CNG_layer")
mal2_cng_map <- readOGR("Corrected_Median_Means_Final_MAL2_CNG_Layer.shp", layer = "Corrected_Median_Means_Final_MAL2_CNG_Layer")
mal2_cng_map <- spTransform(mal2_cng_map, CRS("+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0 "))
mal2_cng <- st_as_sf(mal2_cng_map) 
mal2_cng <- mal2_cng %>%
  data.frame(mal2_cng)  %>%
  dplyr::select(Road_ID, Med_CPC) 
names(mal2_cng) <- c("Road_ID", "UFPs_CNG")
mal2_dsl_map <- readOGR("Corrected_Median_Means_Final_MAL2_Diesel_Layer.shp", layer = "Corrected_Median_Means_Final_MAL2_Diesel_Layer")
mal2_dsl_map <- spTransform(mal2_dsl_map, CRS("+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0 "))
mal2_dsl <- st_as_sf(mal2_dsl_map) 
mal2_dsl <- mal2_dsl %>%
  data.frame(mal2_dsl) %>%
  dplyr::select(Road_ID, Med_CPC) 
names(mal2_dsl) <- c("Road_ID", "UFPs_Dsl")
MAL2_final <- left_join(mal2_cng, mal2_dsl, by = "Road_ID")
MAL2_final$Road_ID <- NULL

```

## Summary of the data

**Using Median of Means map for CNG car with 21 passes.**

```{r fig.align = "center", warning = FALSE, message = FALSE, fig.cap = "\\label{fig:figs}Fig 17: Frequency distribution for the CNG Median of Means map"}
y <- ggplot(data = MAL2_final, aes(x = UFPs_CNG)) + geom_histogram(colour = "#b87333", fill = "#b87333") +
  theme_classic() + labs(x = "UFPs_CNG", y = "count") +
  scale_x_continuous() +
  scale_y_continuous() +
  theme(legend.text = element_text(size = 14),
        plot.subtitle = element_text(size = 10, face = "bold"), 
        axis.title = element_text(size = 18, colour = "black", face = "bold"), 
        axis.text = element_text(size = 14, colour = "black", face = "bold"),
        panel.border = element_rect(colour = "black", fill = NA, size = 1), 
        legend.position = "none",
        strip.background = element_blank(), strip.text = element_blank()) + 
  geom_text(aes(label = paste("N = ",sum(!is.na(MAL2_final$UFPs_CNG)))), x = Inf, y = Inf, hjust = 1, vjust = 2, colour = "black", size = 7) 
y
```

**Using Median of Means map for Diesel car with 5 passes.**

```{r fig.align = "center", warning = FALSE, message = FALSE, fig.cap = "\\label{fig:figs}Fig 18: Frequency distribution for the Diesel Median of Means map"}
y <- ggplot(data = MAL2_final, aes(x = UFPs_Dsl)) + geom_histogram(colour = "#b87333", fill = "#b87333") +
  theme_classic() + labs(x = "UFPs_Dsl", y = "count") +
  scale_x_continuous(limits = c(0, NA), expand = c(0, 0)) +
  scale_y_continuous() +
  theme(legend.text = element_text(size = 14),
        plot.subtitle = element_text(size = 10, face = "bold"), 
        axis.title = element_text(size = 18, colour = "black", face = "bold"), 
        axis.text = element_text(size = 14, colour = "black", face = "bold"),
        panel.border = element_rect(colour = "black", fill = NA, size = 1), 
        legend.position = "none",
        strip.background = element_blank(), strip.text = element_blank()) + 
  geom_text(aes(label = paste("N = ",sum(!is.na(MAL2_final$UFPs_Dsl)))), x = Inf, y = Inf, hjust = 1, vjust = 2, colour = "black", size = 7)
y
```

```{r cols.print = 13}
names(MAL2_final) <- c("UFPs_CNG",  "UFPs_Dsl")
columns <-c("UFPs_CNG",  "UFPs_Dsl")
MAL2_final$UFPs_CNG <- as.numeric(as.character(MAL2_final$UFPs_CNG))
MAL2_final$UFPs_Dsl <- as.numeric(as.character(MAL2_final$UFPs_Dsl))
tmp <- do.call(data.frame,
               list(Mean = apply(MAL2_final, 2, mean, na.rm = TRUE),
                    SD = apply(MAL2_final, 2, sd, na.rm = TRUE), 
                    Median = apply(MAL2_final, 2, median, na.rm = TRUE),
                    IQR = apply(MAL2_final, 2, IQR, na.rm = TRUE),
                    Min = apply(MAL2_final, 2, min, na.rm = TRUE),
                    Max = apply(MAL2_final, 2, max, na.rm = TRUE),
                    p1 = apply(MAL2_final, 2, quantile, probs = c(0.01), na.rm = TRUE),
                    p10 = apply(MAL2_final, 2, quantile, probs = c(0.1), na.rm = TRUE),
                    p25 = apply(MAL2_final, 2, quantile, probs = c(0.25), na.rm = TRUE),
                    p75 = apply(MAL2_final, 2, quantile, probs = c(0.75), na.rm = TRUE),
                    p90 = apply(MAL2_final, 2, quantile, probs = c(0.9),  na.rm = TRUE),
                    p99 = apply(MAL2_final, 2, quantile, probs = c(0.99), na.rm = TRUE),
                    Total_non_NA = apply(MAL2_final, 2, function(x) { length(which(!is.na(x))) })))
tmp$Mean <- round(as.numeric(tmp$Mean), digits = 2)
tmp$IQR <- round(as.numeric(tmp$IQR), digits = 2)
tmp$Median <- round(as.numeric(tmp$Median), digits = 2)
tmp$Min <- round(as.numeric(tmp$Min), digits = 2)
tmp$Max <- round(as.numeric(tmp$Max), digits = 2)
tmp$p10 <- round(as.numeric(tmp$p10), digits = 2)
tmp$SD <- round(as.numeric(tmp$SD), digits = 2)
tmp$p90 <- round(as.numeric(tmp$p90), digits = 2)
tmp$p75 <- round(as.numeric(tmp$p75), digits = 2)
tmp$p99 <- round(as.numeric(tmp$p99), digits = 2)
tmp$p1 <- round(as.numeric(tmp$p1), digits = 2)
tmp$p25 <- round(as.numeric(tmp$p25), digits = 2)
tmp

```

## Median of means map in Malleshwaram 2 for CNG car

```{r fig.align = "center", fig.cap = "\\label{fig:figs}Fig 19: CNG Median of Means map"}
leaflet(mal2_cng_map) %>% 
  addProviderTiles(providers$Stamen.TonerLite) %>%
  addPolylines(weight = 7, color = ~pal(mal2_cng_map$Med_CPC)) %>%
      addLegend("bottomright", pal = pal, values = ~mal2_cng_map$Med_CPC,  title = paste("CNG UFPs Map")) 
 
```

## Median of means map in Malleshwaram 2 for Diesel car

```{r fig.align = "center", fig.cap = "\\label{fig:figs}Fig 20: Diesel Median of Means map"}
leaflet(mal2_dsl_map) %>% 
  addProviderTiles(providers$Stamen.TonerLite) %>%
  addPolylines(weight = 7, color = ~pal(mal2_dsl_map$Med_CPC)) %>%
      addLegend("bottomright", pal = pal, values = ~mal2_dsl_map$Med_CPC,  title = paste("Diesel UFPs Map")) 
```

## t-test for UFPs_CNG and UFPs_Dsl data

```{r message = FALSE, warning = FALSE}
t_test <- t.test(MAL2_final$UFPs_CNG, MAL2_final$UFPs_Dsl)
a <- t_test$p.value
b <- round(t_test$estimate[1], digits = 2)
c <- round(t_test$estimate[2], digits = 2)
e <- round(as.numeric(t_test$parameter), digits = 2)
f <- round(as.numeric(t_test$statistic), digits = 2)
t_test
```


# Area-wise distribution of UFPs 

**Area wise box plots Using the Median of means reference layer (Combined MAL1 and MAL2).**

```{r message = FALSE, warning = FALSE, fig.align = "center", fig.cap = "\\label{fig:figs}Fig 21: Area wise box plot (MAL combined)"}
f <- function(x) {
  r <- quantile(x, probs = c(0.05, 0.25, 0.5, 0.75, 0.95))
  names(r) <- c("ymin", "lower", "middle", "upper", "ymax")
  r
}
final <- final1
final$Area <- substr(final$UID, 1, 3)
final2 <- final
final2$Area <- "Total"
final3 <- rbind(final, final2)
melt_joined_final <- reshape2::melt(final3, id.var = c("UID", "Area"), 
                                    vars = c("UFPs_CNG", "UFPs_Dsl"))
names(melt_joined_final) <- c("UID", "Area", "Car", "Value")
melt_joined_final$Area <- as.vector(melt_joined_final$Area) 
melt_joined_final$Area <- factor(melt_joined_final$Area, levels = c("CBD","KAN", "MAL", "Total"))

plot_box2 <- ggplot(melt_joined_final, aes(x = Area, y = Value, colour = Car)) +   labs(x = "", y = "UFPs") +
  stat_summary(fun.data = f, geom ="boxplot", width = 0.4, size = 0.8, 
               position = position_dodge(width = 0.6)) +  
  stat_summary(fun.y = mean, geom = "point", size = 2, 
               position = position_dodge(width = 0.6)) +
  scale_y_continuous() + theme_classic() +
  scale_color_manual(labels = c("CNG", "Diesel"), values = c("#b87333", "steelblue")) +
  theme(legend.title = element_blank(),
        legend.position = "bottom",
        legend.text = element_text(size = 14, colour = "black", face = "bold"),
        plot.subtitle = element_text(size = 10, face = "bold"), 
        axis.title = element_text(size = 18, colour = "black", face = "bold"), 
        axis.text = element_text(size = 14, colour = "black", face = "bold"),
        panel.border = element_rect(colour = "black", fill = NA, size = 1), 
        strip.background = element_blank(), strip.text = element_blank()) 

plot_box2
```



```{r message = FALSE, warning = FALSE, fig.align = "center", fig.cap = "\\label{fig:figs}Fig 22: Area wise box plot (MAL split)"}
final <- final1
final$Area <- substr(final$UID, 1, 4)
final$Area <- gsub("_", "", final$Area)
final2 <- final
final2$Area <- "Total"
final3 <- rbind(final, final2)
melt_joined_final <- reshape2::melt(final3, id.var = c("UID", "Area"), 
                                    vars = c("UFPs_CNG", "UFPs_Dsl"))
names(melt_joined_final) <- c("UID", "Area", "Car", "Value")
melt_joined_final$Area <- as.vector(melt_joined_final$Area) 
melt_joined_final$Area <- factor(melt_joined_final$Area, levels = c("CBD","KAN", "MAL1", "MAL2", "Total"))

plot_box2 <- ggplot(melt_joined_final, aes(x = Area, y = Value, colour = Car)) +   labs(x = "", y = "UFPs") +
  stat_summary(fun.data = f, geom ="boxplot", width = 0.4, size = 0.8, 
               position = position_dodge(width = 0.6)) +  
  stat_summary(fun.y = mean, geom = "point", size = 2, 
               position = position_dodge(width = 0.6)) +
  scale_y_continuous() + theme_classic() +
  scale_color_manual(labels = c("CNG", "Diesel"), values = c("#b87333", "steelblue")) +
  theme(legend.title = element_blank(),
        legend.position = "bottom",
        legend.text = element_text(size = 14, colour = "black", face = "bold"),
        plot.subtitle = element_text(size = 10, face = "bold"), 
        axis.title = element_text(size = 18, colour = "black", face = "bold"), 
        axis.text = element_text(size = 14, colour = "black", face = "bold"),
        panel.border = element_rect(colour = "black", fill = NA, size = 1), 
        strip.background = element_blank(), strip.text = element_blank()) + 
  annotate(geom = "text", label = "p < 0.05", x = "Total", y = 150, size = 5) + 
  annotate(geom = "text", label = "p > 0.05", x = "MAL1", y = 150, size = 5) + 
  annotate(geom = "text", label = "p > 0.05", x = "MAL2", y = 150, size = 5) + 
  annotate(geom = "text", label = "p < 0.05", x = "KAN", y = 150, size = 5) + 
  annotate(geom = "text", label = "p < 0.05", x = "CBD", y = 150, size = 5)

plot_box2
```




